\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-08-13 doc/sui14/applications.tex
adding tasks for applications
added some commas

Our prototype includes three smart devices: a lamp and a fan that could be switched on and off; a smart TV with playback, volume and navigation controls (see Figure~\ref{fig:smart-home}). The on/off appliances are using relays, and the smart TV is a 30\inch{} display connected to a laptop. User interfaces for each were pre-defined in our application.
%
We set the devices up in a simulated living room environment and invited 14 users to step through a predefined set of tasks to control the appliances at a distance.

>>>>

Our prototype, \changes{(based on {\em Naive IR}, \footnote{For this particular configuration, the environment is not dense enough, and {\em Naive IR} performs well for head orientation based targeting proof-of-concept.})} includes three smart devices: a lamp and a fan that could be switched on and off; a smart TV with playback, volume and navigation controls (see Figure~\ref{fig:smart-home}). The on/off appliances are using relays, and the smart TV is a 30\inch{} display connected to a laptop. User interfaces for each were pre-defined in our application.

%
We set the devices up in a simulated living room environment and invited 14 users to step through a predefined set of tasks to control the appliances at a distance. \changes{These tasks include turning off the light, playing movie, turning up the volume, etc., which are some sample tasks that people would normally do at home.}

%% set of predefined tasks:
% \item Turn off the lights as you want to watch the movie in a darkened room.
% \item You feel a little hot in the room, so you turn on the fan.
% \item You connect to the Smart TV and start playing the movie. 
% \item The volume seems too soft to hear over the fan- turn it up a bit. 
% \item After a while, you want to take a break to get a snack. Pause the movie. 
% \item When you come back, you've forgotten what was said last - rewind by ~30 seconds and restart the movie. 
% \item When the credits roll, you stop the movie and turn the lights back on.
% \item After awhile, you turn off the fan and leave the room.
